\begin{algorithm}
\caption{INIT-VAULT}
\begin{algorithmic}
  \COMMENT{Pointer to vault account.}
  \INPUT $r_1$ = acct
  \COMMENT{Pointer to REGISTER-MARKET stack frame.}
  \INPUT $r_2$ = frame
  \REQUIRE frame.vault\_index $\in$ \{
    \texttt{register\_misc.VAULT\_INDEX\_BASE},
    \texttt{register\_misc.VAULT\_INDEX\_QUOTE}
  \}
  \REQUIRE frame.token\_program\_is\_2022 $\in$ \{
    \texttt{true},
    \texttt{false}
  \}
  \REQUIRE *frame.mint $\in$ \{
    input.base\_mint,
    input\_shifted.quote\_mint
  \}
  \REQUIRE frame.token\_program\_id
  \REQUIRE frame.program\_id
  \REQUIRE frame.input
  \REQUIRE frame.lamports\_per\_byte
  \REQUIRE frame.pda\_seeds[0].len = \texttt{Address.size}
  \REQUIRE frame.pda\_seeds[2].addr = \&frame.bump
  \REQUIRE frame.pda\_seeds[2].len = \texttt{u8.size}
  \REQUIRE *frame.system\_program\_id = input.system\_program.address
  \REQUIRE frame.signers\_seeds.addr = \&frame.pda\_seeds
  \REQUIRE frame.signers\_seeds.len = \texttt{RegisterMarketFrame.PDA\_SEEDS\_N\_SEEDS}
  \REQUIRE input.user.data\_len = \texttt{data.LEN\_ZERO}
  \REQUIRE frame.cpi[0].info.executable = \texttt{false}
\FUNCTION{INIT-VAULT}{acct, frame}
  \STATE \CALL{Store}{frame}
  \STATE \CALL{Store}{acct}
  \COMMENT{Derive vault PDA.}
  \STATE frame.pda\_seeds[0].addr = \&input.market.address
  \STATE frame.pda\_seeds[1].addr = \&frame.vault\_index
  \STATE frame.pda\_seeds[1].len = \texttt{u8.size}
  \STATE syscall.seeds = \&frame.pda\_seeds
  \STATE syscall.seeds\_len = \texttt{register\_misc.TRY\_FIND\_VAULT\_PDA\_SEEDS\_LEN}
  \STATE syscall.program\_id = frame.program\_id
  \STATE syscall.program\_address = \&frame.pda
  \STATE syscall.bump\_seed = \&frame.bump
  \STATE \CALL{sol-try-find-program-address}{}
  \COMMENT{Verify vault address matches derived PDA.}
  \IF{acct.address $\neq$ frame.pda}
    \IF{frame.vault\_index == \texttt{register\_misc.VAULT\_INDEX\_BASE}}
      \RETURN \texttt{ErrorCode::InvalidBaseVaultPubkey}
    \ELSE
      \RETURN \texttt{ErrorCode::InvalidQuoteVaultPubkey}
    \ENDIF
  \ENDIF
  \COMMENT{Determine token account size.}
  \IF{frame.token\_program\_is\_2022}
    \COMMENT{Set up mint as CPI account.}
    \STATE frame.cpi[0].info.is\_signer = \texttt{false}
    \STATE frame.cpi[0].info.is\_writable = \texttt{false}
    \STATE frame.cpi[0].meta.is\_signer = \texttt{false}
    \STATE frame.cpi[0].meta.is\_writable = \texttt{false}
    \STATE frame.cpi[0].meta.pubkey = \&mint.address
    \STATE frame.cpi[0].info.key = \&mint.address
    \STATE frame.cpi[0].info.owner = \&mint.owner
    \STATE frame.cpi[0].info.lamports = \&mint.lamports
    \STATE frame.cpi[0].info.data\_len = mint.data\_len
    \STATE frame.cpi[0].info.data = \&mint.data
    \COMMENT{Populate SolInstruction for GetAccountDataSize CPI.}
    \STATE frame.sol\_instruction.program\_id = frame.token\_program\_id
    \STATE frame.sol\_instruction.accounts = \&frame.cpi[0].meta
    \STATE frame.sol\_instruction.account\_len =
      \texttt{token.GET\_ACCOUNT\_DATA\_SIZE\_N\_ACCOUNTS}
    \STATE frame.get\_account\_data\_size\_data =
      \texttt{token.GET\_ACCOUNT\_DATA\_SIZE\_DISC}
    \STATE frame.sol\_instruction.data = \&frame.get\_account\_data\_size\_data
    \STATE frame.sol\_instruction.data\_len = \texttt{u8.size}
    \COMMENT{Invoke GetAccountDataSize CPI (no signers).}
    \STATE syscall.instruction = \&frame.sol\_instruction
    \STATE syscall.account\_infos = \&frame.cpi[0].info
    \STATE syscall.account\_infos\_len =
      \texttt{token.GET\_ACCOUNT\_DATA\_SIZE\_N\_ACCOUNTS}
    \STATE syscall.seeds\_len = \texttt{token.GET\_ACCOUNT\_DATA\_SIZE\_N\_SEEDS}
    \STATE \CALL{sol-invoke-signed-c}{}
    \COMMENT{Get return data.}
    \STATE syscall.bytes = \&frame.token\_account\_data\_size
    \STATE syscall.bytes\_len = \texttt{u64.size}
    \STATE syscall.program\_id = \&frame.get\_return\_data\_program\_id
    \STATE \CALL{sol-get-return-data}{}
    \STATE acct\_size = frame.token\_account\_data\_size
    \COMMENT{Override default return data nonzero return code.}
    \STATE result = \texttt{entrypoint.RETURN\_SUCCESS}
  \ELSE
    \STATE acct\_size = \texttt{token.ACCOUNT\_SIZE}
  \ENDIF
  \COMMENT{Prepare CreateAccount instruction fields.}
  \STATE acct\_size = acct\_size + \texttt{account.STORAGE\_OVERHEAD}
  \STATE frame.create\_account\_data.lamports =
    acct\_size $\times$ frame.lamports\_per\_byte
  \STATE frame.create\_account\_data.space = acct\_size
  \STATE frame.create\_account\_data.owner = frame.token\_program\_id
  \COMMENT{Assign CPI account fields via immediates.}
  \STATE frame.cpi[0].info.is\_signer = \texttt{true}
  \STATE frame.cpi[0].info.is\_writable = \texttt{true}
  \STATE frame.cpi[0].meta.is\_signer = \texttt{true}
  \STATE frame.cpi[0].meta.is\_writable = \texttt{true}
  \STATE frame.cpi[1].info.is\_signer = \texttt{true}
  \STATE frame.cpi[1].info.is\_writable = \texttt{true}
  \STATE frame.cpi[1].meta.is\_signer = \texttt{true}
  \STATE frame.cpi[1].meta.is\_writable = \texttt{true}
  \STATE frame.cpi[0].info.data\_len = \texttt{data.LEN\_ZERO}
  \STATE frame.cpi[1].info.data\_len = acct.data\_len
  \COMMENT{Assign CPI account fields via pointers.}
  \STATE frame.cpi[0].meta.pubkey = \&input.user.address
  \STATE frame.cpi[0].info.key = \&input.user.address
  \STATE frame.cpi[0].info.owner = \&input.user.owner
  \STATE frame.cpi[0].info.lamports = \&input.user.lamports
  \STATE frame.cpi[0].info.data = \&input.user.data
  \STATE frame.cpi[1].meta.pubkey = \&acct.address
  \STATE frame.cpi[1].info.key = \&acct.address
  \STATE frame.cpi[1].info.owner = \&acct.owner
  \STATE frame.cpi[1].info.lamports = \&acct.lamports
  \STATE frame.cpi[1].info.data = \&acct.data
  \COMMENT{Populate SolInstruction for CreateAccount CPI.}
  \STATE frame.sol\_instruction.program\_id = frame.system\_program\_id
  \STATE frame.sol\_instruction.accounts = \&frame.cpi.account\_metas
  \STATE frame.sol\_instruction.account\_len =
    \texttt{register\_misc.CREATE\_ACCOUNT\_N\_ACCOUNTS}
  \STATE frame.sol\_instruction.data = \&frame.create\_account\_data
  \STATE frame.sol\_instruction.data\_len = \texttt{CreateAccountData.size}
  \COMMENT{Invoke CreateAccount CPI.}
  \STATE syscall.instruction = \&frame.sol\_instruction
  \STATE syscall.account\_infos = \&frame.cpi.account\_infos
  \STATE syscall.account\_infos\_len =
    \texttt{register\_misc.CREATE\_ACCOUNT\_N\_ACCOUNTS}
  \STATE syscall.seeds = \&frame.signers\_seeds
  \STATE syscall.seeds\_len = \texttt{register\_misc.N\_PDA\_SIGNERS}
  \STATE \CALL{sol-invoke-signed-c}{}
\ENDFUNCTION
\end{algorithmic}
\end{algorithm}
