\begin{algorithm}
\caption{REGISTER-MARKET}
\begin{algorithmic}
  \COMMENT{Pointer to input buffer.}
  \INPUT $r_1$ = input
  \COMMENT{Pointer to instruction data.}
  \INPUT $r_2$ = insn
  \COMMENT{Number of accounts.}
  \INPUT $r_3$ = n\_accounts
  \COMMENT{Instruction data length.}
  \INPUT $r_4$ = insn\_len
  \REQUIRE insn.discriminant == \texttt{Discriminant::RegisterMarket}
\PROCEDURE{REGISTER-MARKET}{input, insn, n\_accounts, insn\_len}
  \COMMENT{Check number of accounts and instruction data length.}
  \IF{n\_accounts $<$ \texttt{RegisterMarketAccounts.LEN}}
    \RETURN \texttt{ErrorCode::InvalidNumberOfAccounts}
  \ENDIF
  \IF{insn\_len $\neq$ \texttt{RegisterMarketData.LEN}}
    \RETURN \texttt{ErrorCode::InvalidInstructionLength}
  \ENDIF
  \COMMENT{Check user, market accounts.}
  \IF{input.user.data\_len $\neq$ 0}
    \RETURN \texttt{ErrorCode::UserHasData}
  \ENDIF
  \IF{input.market.duplicate $\neq$ \texttt{account.NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::MarketAccountIsDuplicate}
  \ENDIF
  \IF{input.market.data\_len $\neq$ 0}
    \RETURN \texttt{ErrorCode::MarketHasData}
  \ENDIF
  \COMMENT{Check base mint account, create signer seed.}
  \IF{input.base\_mint.duplicate $\neq$ \texttt{account.NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::BaseMintIsDuplicate}
  \ENDIF
  \STATE frame.pda\_seeds[0].addr = input.base\_mint.pubkey
  \STATE frame.pda\_seeds[0].len = \texttt{Address.size}
  \COMMENT{Increment input buffer by base mint padded data length for quote offsets.}
  \STATE input\_shifted = input + input.base\_mint.padded\_data\_len
  \STATE frame.input\_shifted = input\_shifted
  \COMMENT{Check quote mint account, create signer seed.}
  \IF{input\_shifted.quote\_mint.duplicate $\neq$ \texttt{account.NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::QuoteMintIsDuplicate}
  \ENDIF
  \STATE frame.pda\_seeds[1].addr = input\_shifted.quote\_mint.pubkey
  \STATE frame.pda\_seeds[1].len = \texttt{Address.size}
  \COMMENT{Advance to System Program account.}
  \STATE quote\_mint\_padded\_data\_len = input\_shifted.quote\_mint.padded\_data\_len
  \STATE acct = \&input\_shifted.quote\_mint
  \STATE acct += quote\_mint\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Derive market PDA.}
  \STATE frame.input = input
  \STATE syscall.seeds = \&frame.pda\_seeds
  \STATE syscall.program\_id = \&insn.program\_id
  \STATE syscall.seeds\_len = \texttt{register\_misc.TRY\_FIND\_MARKET\_PDA\_SEEDS\_LEN}
  \STATE syscall.program\_address = \&frame.pda
  \STATE syscall.bump\_seed = \&frame.bump
  \STATE \CALL{sol-try-find-program-address}{}
  \COMMENT{Verify derived market PDA matches market account pubkey.}
  \STATE input = frame.input
  \IF{input.market.pubkey $\neq$ frame.market\_pda}
    \RETURN \texttt{ErrorCode::InvalidMarketPubkey}
  \ENDIF
  \COMMENT{Populate bump signer seed from derived bump.}
  \STATE frame.pda\_seeds[2].addr = \&syscall.bump\_seed
  \STATE frame.pda\_seeds[2].len = \texttt{u8.size}
  \COMMENT{Populate CreateAccount CPI instruction data owner field.}
  \STATE frame.create\_account\_data.owner = syscall.program\_id
  \COMMENT{Check System Program account.}
  \IF{acct.duplicate $\neq$ \texttt{account.NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::SystemProgramIsDuplicate}
  \ENDIF
  \IF{acct.pubkey $\neq$ frame.system\_program\_pubkey}
    \RETURN \texttt{ErrorCode::InvalidSystemProgramPubkey}
  \ENDIF
  \COMMENT{Populate CPI program ID field.}
  \STATE frame.sol\_instruction.program\_id = \&acct.address
  \COMMENT{Advance to Rent sysvar account.}
  \STATE system\_program\_padded\_data\_len = acct.padded\_data\_len
  \STATE acct += system\_program\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Check Rent sysvar account.}
  \IF{acct.duplicate $\neq$ \texttt{account.NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::RentSysvarIsDuplicate}
  \ENDIF
  \IF{acct.pubkey $\neq$ \texttt{pubkey.RENT}}
    \RETURN \texttt{ErrorCode::InvalidRentSysvarPubkey}
  \ENDIF
  \COMMENT{Prepare CreateAccount instruction lamports, space fields.}
  \STATE frame.create\_account\_data.space = \texttt{MarketHeader.size}
  \STATE acct\_size = \texttt{MarketHeader.size} + \texttt{account.STORAGE\_OVERHEAD}
  \STATE lamports\_per\_byte = acct.data.lamports\_per\_byte
  \STATE frame.create\_account\_data.lamports = acct\_size $\times$ lamports\_per\_byte
  \COMMENT{Advance to base token program account.}
  \STATE rent\_sysvar\_padded\_data\_len = acct.padded\_data\_len
  \STATE acct += rent\_sysvar\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Assign CPI account fields via immediates.}
  \STATE frame.cpi[0].info.is\_signer = \texttt{true}
  \STATE frame.cpi[0].info.is\_writable = \texttt{true}
  \STATE frame.cpi[0].meta.is\_signer = \texttt{true}
  \STATE frame.cpi[0].meta.is\_writable = \texttt{true}
  \STATE frame.cpi[1].info.is\_signer = \texttt{true}
  \STATE frame.cpi[1].info.is\_writable = \texttt{true}
  \STATE frame.cpi[1].meta.is\_signer = \texttt{true}
  \STATE frame.cpi[1].meta.is\_writable = \texttt{true}
  \COMMENT{Assign CPI account fields via pointers.}
  \STATE frame.cpi[0].meta.pubkey = \&input.user.address
  \STATE frame.cpi[0].info.key = \&input.user.address
  \STATE frame.cpi[0].info.owner = \&input.user.owner
  \STATE frame.cpi[0].info.lamports = \&input.user.lamports
  \STATE frame.cpi[0].info.data = \&input.user.data
  \STATE frame.cpi[1].meta.pubkey = \&input.market.address
  \STATE frame.cpi[1].info.key = \&input.market.address
  \STATE frame.cpi[1].info.owner = \&input.market.owner
  \STATE frame.cpi[1].info.lamports = \&input.market.lamports
  \STATE frame.cpi[1].info.data = \&input.market.data
  \COMMENT{Populate signers seeds for CPI.}
  \STATE frame.signers\_seeds.addr = \&frame.pda\_seeds
  \STATE frame.signers\_seeds.len = \texttt{RegisterMarketFrame.PDA\_SEEDS\_N\_SEEDS}
  \COMMENT{Populate SolInstruction for CreateAccount CPI.}
  \STATE frame.sol\_instruction.accounts = \&frame.cpi.account\_metas
  \STATE frame.sol\_instruction.account\_len =
    \texttt{register\_misc.CREATE\_ACCOUNT\_N\_ACCOUNTS}
  \STATE frame.sol\_instruction.data = \&frame.create\_account\_data
  \STATE frame.sol\_instruction.data\_len = \texttt{CreateAccountData.size}
  \COMMENT{Invoke CreateAccount CPI.}
  \STATE syscall.instruction = \&frame.sol\_instruction
  \STATE syscall.account\_infos = \&frame.cpi.account\_infos
  \STATE syscall.account\_infos\_len =
    \texttt{register\_misc.CREATE\_ACCOUNT\_N\_ACCOUNTS}
  \STATE syscall.seeds = \&frame.signers\_seeds
  \STATE syscall.seeds\_len = \texttt{register\_misc.N\_PDA\_SIGNERS}
  \STATE \CALL{sol-invoke-signed-c}{}
  \COMMENT{Retrieve input buffer pointers.}
  \STATE input = frame.input
  \STATE input\_shifted = frame.input\_shifted
  \COMMENT{Check base token program account.}
  \IF{acct.duplicate $\neq$ \texttt{account.NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::BaseTokenProgramIsDuplicate}
  \ENDIF
  \COMMENT{Verify base token program owns the base mint.}
  \IF{acct.pubkey $\neq$ input.base\_mint.owner}
    \RETURN \texttt{ErrorCode::BaseTokenProgramNotBaseMintOwner}
  \ENDIF
  \COMMENT{Verify base token program is Token Program or Token 2022.}
  \IF{acct.pubkey $\neq$ \texttt{pubkey.TOKEN\_PROGRAM}}
    \IF{acct.pubkey $\neq$ \texttt{pubkey.TOKEN\_2022\_PROGRAM}}
      \RETURN \texttt{ErrorCode::BaseTokenProgramNotTokenProgram}
    \ENDIF
  \ENDIF
  \COMMENT{Derive base vault PDA from base token program.}
  \STATE frame.pda\_seeds[0].addr = \&input.market.address
  \STATE frame.vault\_index = \texttt{register\_misc.VAULT\_INDEX\_BASE}
  \STATE frame.pda\_seeds[1].addr = \&frame.vault\_index
  \STATE frame.pda\_seeds[1].len = \texttt{u8.size}
  \STATE syscall.seeds = \&frame.pda\_seeds
  \STATE syscall.seeds\_len = \texttt{register\_misc.TRY\_FIND\_VAULT\_PDA\_SEEDS\_LEN}
  \STATE syscall.program\_id = \&acct.address
  \STATE syscall.program\_address = \&frame.pda
  \STATE syscall.bump\_seed = \&frame.bump
  \STATE \CALL{sol-try-find-program-address}{}
  \COMMENT{Advance to base vault account.}
  \STATE base\_token\_program\_padded\_data\_len = acct.padded\_data\_len
  \STATE acct += base\_token\_program\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Verify base vault address matches derived PDA.}
  \IF{acct.pubkey $\neq$ frame.pda}
    \RETURN \texttt{ErrorCode::InvalidBaseVaultPubkey}
  \ENDIF
  \COMMENT{Advance to quote token program account.}
  \STATE base\_vault\_padded\_data\_len = acct.padded\_data\_len
  \STATE acct += base\_vault\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Check quote token program account.}
  \IF{acct.duplicate == \texttt{account.NON\_DUP\_MARKER}}
    \COMMENT{Non-duplicate; verify quote token program owns the quote mint.}
    \IF{acct.pubkey $\neq$ input\_shifted.quote\_mint.owner}
      \RETURN \texttt{ErrorCode::NonDupQuoteTokenProgramNotQuoteMintOwner}
    \ENDIF
    \COMMENT{Verify quote token program is Token Program or Token 2022.}
    \IF{acct.pubkey $\neq$ \texttt{pubkey.TOKEN\_PROGRAM}}
      \IF{acct.pubkey $\neq$ \texttt{pubkey.TOKEN\_2022\_PROGRAM}}
        \RETURN \texttt{ErrorCode::QuoteTokenProgramNotTokenProgram}
      \ENDIF
    \ENDIF
    \COMMENT{Update syscall program ID from non-duplicate quote token program.}
    \STATE syscall.program\_id = \&acct.address
    \COMMENT{Advance to quote vault account.}
    \STATE quote\_token\_program\_padded\_data\_len = acct.padded\_data\_len
    \STATE acct += quote\_token\_program\_padded\_data\_len + \texttt{EmptyAccount.size}
  \ELSE
    \COMMENT{Duplicate; verify position is base token program.}
    \IF{acct.duplicate $\neq$ \texttt{RegisterMarketAccounts::BaseTokenProgram}}
      \RETURN \texttt{ErrorCode::InvalidQuoteTokenProgramDuplicate}
    \ENDIF
    \COMMENT{Verify duplicate owns the quote mint.}
    \IF{input.base\_mint.owner $\neq$ input\_shifted.quote\_mint.owner}
      \RETURN \texttt{ErrorCode::DupQuoteTokenProgramNotQuoteMintOwner}
    \ENDIF
    \COMMENT{Advance to quote vault account.}
    \STATE acct += \texttt{u64.size}
  \ENDIF
  \COMMENT{Derive quote vault PDA.}
  \STATE frame.vault\_index = \texttt{register\_misc.VAULT\_INDEX\_QUOTE}
  \STATE \CALL{sol-try-find-program-address}{}
  \COMMENT{Verify quote vault address matches derived PDA.}
  \IF{acct.pubkey $\neq$ frame.pda}
    \RETURN \texttt{ErrorCode::InvalidQuoteVaultPubkey}
  \ENDIF
\ENDPROCEDURE
\end{algorithmic}
\end{algorithm}
