\begin{algorithm}
\caption{REGISTER-MARKET}
\begin{algorithmic}
  \COMMENT{Pointer to input buffer.}
  \INPUT $r_1$ = input
  \COMMENT{Pointer to instruction data.}
  \INPUT $r_2$ = insn
  \COMMENT{Number of accounts.}
  \INPUT $r_3$ = n\_accounts
  \COMMENT{Instruction data length.}
  \INPUT $r_4$ = insn\_len
  \COMMENT{Pointer to stack frame.}
  \INPUT $r_{10}$ = frame
  \REQUIRE insn.discriminant == \texttt{Discriminant::RegisterMarket}
\PROCEDURE{REGISTER-MARKET}{input, insn, n\_accounts, insn\_len, frame}
  \COMMENT{Check number of accounts and instruction data length.}
  \IF{n\_accounts $<$ \texttt{Accounts.count}}
    \RETURN \texttt{ErrorCode::InvalidNumberOfAccounts}
  \ENDIF
  \IF{insn\_len $\neq$ \texttt{Data.size}}
    \RETURN \texttt{ErrorCode::InvalidInstructionLength}
  \ENDIF
  \STATE frame.program\_id = \&insn.program\_id
  \COMMENT{Check user, market accounts.}
  \IF{input.user.data\_len $\neq$ 0}
    \RETURN \texttt{ErrorCode::UserHasData}
  \ENDIF
  \IF{input.market.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::MarketAccountIsDuplicate}
  \ENDIF
  \IF{input.market.data\_len $\neq$ 0}
    \RETURN \texttt{ErrorCode::MarketHasData}
  \ENDIF
  \COMMENT{Check base mint account.}
  \IF{input.base\_mint.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::BaseMintIsDuplicate}
  \ENDIF
  \COMMENT{Increment input buffer by base mint padded data length for quote offsets.}
  \STATE input\_shifted = input + input.base\_mint.padded\_data\_len
  \STATE frame.input\_shifted = input\_shifted
  \COMMENT{Check quote mint account.}
  \IF{input\_shifted.quote\_mint.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::QuoteMintIsDuplicate}
  \ENDIF
  \COMMENT{Advance to System Program account.}
  \STATE quote\_mint\_padded\_data\_len = input\_shifted.quote\_mint.padded\_data\_len
  \STATE acct = \&input\_shifted.quote\_mint
  \STATE acct += quote\_mint\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Check System Program account.}
  \IF{acct.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::SystemProgramIsDuplicate}
  \ENDIF
  \IF{acct.address $\neq$ frame.system\_program\_pubkey}
    \RETURN \texttt{ErrorCode::InvalidSystemProgramPubkey}
  \ENDIF
  \STATE frame.system\_program\_id = \&acct.address
  \COMMENT{Advance to Rent sysvar account.}
  \STATE system\_program\_padded\_data\_len = acct.padded\_data\_len
  \STATE acct += system\_program\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Check Rent sysvar account.}
  \IF{acct.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::RentSysvarIsDuplicate}
  \ENDIF
  \IF{acct.address $\neq$ \texttt{common::pubkey::RENT}}
    \RETURN \texttt{ErrorCode::InvalidRentSysvarPubkey}
  \ENDIF
  \STATE frame.rent = acct
  \COMMENT{Derive market PDA, populate CPI fields, invoke CreateAccount.}
  \STATE \CALL{INIT-MARKET-PDA}{input, insn, acct, frame}
  \COMMENT{Retrieve input buffer pointers and advance to base token program account.}
  \STATE input = frame.input
  \STATE input\_shifted = frame.input\_shifted
  \STATE rent\_sysvar\_padded\_data\_len = acct.padded\_data\_len
  \STATE acct += rent\_sysvar\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Check base token program account.}
  \IF{acct.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::BaseTokenProgramIsDuplicate}
  \ENDIF
  \COMMENT{Verify base token program owns the base mint.}
  \IF{acct.address $\neq$ input.base\_mint.owner}
    \RETURN \texttt{ErrorCode::BaseTokenProgramNotBaseMintOwner}
  \ENDIF
  \COMMENT{Verify base token program is Token Program or Token 2022.}
  \IF{acct.address $\neq$ \texttt{common::pubkey::TOKEN\_PROGRAM}}
    \IF{acct.address $\neq$ \texttt{common::pubkey::TOKEN\_2022\_PROGRAM}}
      \RETURN \texttt{ErrorCode::BaseTokenProgramNotTokenProgram}
    \ENDIF
    \STATE frame.token\_program\_is\_2022 = \texttt{true}
  \ENDIF
  \STATE frame.token\_program\_id = \&acct.address
  \COMMENT{Advance to base vault account.}
  \STATE base\_token\_program\_padded\_data\_len = acct.padded\_data\_len
  \STATE acct += base\_token\_program\_padded\_data\_len + \texttt{EmptyAccount.size}
  \COMMENT{Check base vault account.}
  \IF{acct.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::BaseVaultIsDuplicate}
  \ENDIF
  \IF{acct.data\_len $\neq$ \texttt{common::memory::LEN\_ZERO}}
    \RETURN \texttt{ErrorCode::BaseVaultHasData}
  \ENDIF
  \COMMENT{Initialize base vault account.}
  \STATE frame.vault\_index = \texttt{market::VAULT\_INDEX\_BASE}
  \STATE frame.mint = \&input.base\_mint
  \STATE result = \CALL{INIT-VAULT}{acct, frame}
  \IF{result $\neq$ \texttt{entrypoint::RETURN\_SUCCESS}}
    \RETURN result
  \ENDIF
  \COMMENT{Store derived bump in market account data.}
  \STATE input.market.data.base\_vault\_bump = frame.bump
  \COMMENT{Advance to quote token program account.}
  \STATE acct += \texttt{EmptyAccount.size}
  \COMMENT{Check quote token program account.}
  \IF{acct.duplicate == \texttt{common::account::NON\_DUP\_MARKER}}
    \COMMENT{Non-duplicate; verify quote token program owns the quote mint.}
    \IF{acct.address $\neq$ input\_shifted.quote\_mint.owner}
      \RETURN \texttt{ErrorCode::NonDupQuoteTokenProgramNotQuoteMintOwner}
    \ENDIF
    \COMMENT{Verify quote token program is Token Program or Token 2022.}
    \IF{acct.address $\neq$ \texttt{common::pubkey::TOKEN\_PROGRAM}}
      \IF{acct.address $\neq$ \texttt{common::pubkey::TOKEN\_2022\_PROGRAM}}
        \RETURN \texttt{ErrorCode::QuoteTokenProgramNotTokenProgram}
      \ENDIF
      \STATE frame.token\_program\_is\_2022 = \texttt{true}
    \ELSE
      \STATE frame.token\_program\_is\_2022 = \texttt{false}
    \ENDIF
    \STATE frame.token\_program\_id = \&acct.address
    \COMMENT{Advance to quote vault account.}
    \STATE quote\_token\_program\_padded\_data\_len = acct.padded\_data\_len
    \STATE acct += quote\_token\_program\_padded\_data\_len + \texttt{EmptyAccount.size}
  \ELSE
    \COMMENT{Duplicate; verify position is base token program.}
    \IF{acct.duplicate $\neq$ \texttt{Accounts::BaseTokenProgram}}
      \RETURN \texttt{ErrorCode::InvalidQuoteTokenProgramDuplicate}
    \ENDIF
    \COMMENT{Verify duplicate owns the quote mint.}
    \IF{input.base\_mint.owner $\neq$ input\_shifted.quote\_mint.owner}
      \RETURN \texttt{ErrorCode::DupQuoteTokenProgramNotQuoteMintOwner}
    \ENDIF
    \COMMENT{Advance to quote vault account.}
    \STATE acct += \texttt{u64.size}
  \ENDIF
  \COMMENT{Check quote vault account.}
  \IF{acct.duplicate $\neq$ \texttt{common::account::NON\_DUP\_MARKER}}
    \RETURN \texttt{ErrorCode::QuoteVaultIsDuplicate}
  \ENDIF
  \IF{acct.data\_len $\neq$ \texttt{common::memory::LEN\_ZERO}}
    \RETURN \texttt{ErrorCode::QuoteVaultHasData}
  \ENDIF
  \COMMENT{Initialize quote vault account.}
  \STATE frame.vault\_index = \texttt{market::VAULT\_INDEX\_QUOTE}
  \STATE frame.mint = \&input\_shifted.quote\_mint
  \STATE \CALL{INIT-VAULT}{acct, frame}
  \COMMENT{Store derived bump in market account data.}
  \STATE input.market.data.quote\_vault\_bump = frame.bump
\ENDPROCEDURE
\end{algorithmic}
\end{algorithm}
